---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(BestTransform)
```


# BestTransform: Identify the transformation that best fits all the continous vectors in a given dataframe.



The `BestTransform` R package was designed to help find a transformation that best fits all the continuous vectors in a given dataframe. There are many techniques that have been developed in this aim, however each has been subject to their own strengths/weaknesses, and it is unclear on how to decide which will work best until the data is observed. This package will look at a range of possible transformations and return the best one, based on the user specified metric, wich can be chosen from Minimum skewness, Shapiro P value and Pearson P value. 


## Installation

You can install the most recent (devel) version of BestTransform from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("SrinivasaSaketh/BestTransform")
```

Or, you can download it from CRAN with:

```{r cran-installation, eval = FALSE}
install.packages("BestTransform")
```

## Example

```{r, eval = FALSE}
library(BestTransform)
```

```{r example}
#Load the dataset
data <- iris
#Transform the data
trans <- BestTransform::BestTransform(data, "Species")	

```

